\documentclass[a4paper,margin,line]{resume}
\usepackage[defblank]{paralist}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage[unicode]{hyperref}
\hypersetup{
	pdftitle={Joseph Batchik's Resume},
	pdfauthor={Joseph Batchik},
	pdfborder={0 0 0},
	unicode=true
}


\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
  }

\marginsize{0.375in}{1.875in}{0.375in}{0.375in}
\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{(a)}{(1)}{}{}{}{}
\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[5]{ \item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5} \\*}
\begin{document}
\name{\Large{Joseph D. Batchik} \hskip 0pt plus 2fil minus 0pt {\small{\href{mailto:josephbatchik@gmail.com}{josephbatchik@gmail.com} - (410) 599-3550}}}
\begin{resume}
\section{\mysidestyle Objective}
    To secure full-time employment in a challenging, fast-paced development role.
\section{\mysidestyle Work Experience}
	\begin{asparadesc}
        \employer{Cloudera}{San Francisco, CA}{Summer 2015}{Software Engineer Intern}
        {http://cloudera.com/}
        \small
        Worked on a several different parts of Apache Spark, including implementing performance
        increases which reduce network traffic by over 90\% and integrating Apache
        Avro as a first class citizen into Spark core. Went through the process of packaging
        changes into major Hadoop release. Languages / tools used: 
        Scala, Java, Avro.
        \normalsize
        \\
        \employer{Google}{New York, NY}{Summer 2014}{SRE Engineering Practicum Intern}
        {http://google.com/}
		\small
        Implemented load testing infrastructure for newly released software,
        allowing for early detection of bugs and performance defects before
        releasing to the end user. Reduced request latency by 70\% for 
        back-end monitoring services. Languages / tools used: Java, Python, 
        Protocol Buffers, Google data stores.
		\normalsize
		\\
		\employer{Amazon}{Seattle, WA}{Spring 2014}{Software Developer Engineer Intern}
        {http://amazon.com/}
		\small
	    Overhauled internal search capabilities for the Enterprise Data Warehouse
        team, allowing for near-real time search capabilities for Amazon's data
        analytics. Designed the System to be fault tolerant to preserve data integrity.
        Languages / tools used: Java, various Amazon cloud products, including Cloud-Search
        and SNS.
        \normalsize
		\\
		\employer{John Hopkins University Applied Physics Lab}{Laurel, MD}
        {Summer 2013}{Engineering Intern}{http://jhuapl.edu/}
		\small
		Working with a team, developed a sensor management system used to control and collect data from
        multiple telescopes remotely. Languages / tools used: Java, ant, svn, SQL,
        Google Protocol Buffers.
        \normalsize
        \\
        \\
        Additional prior summer internships:\\
        \textbf{Six3 Systems, Inc.} - Fulton, MD \hfill Summer 2012 - http://six3esd.com \\
        \textbf{SRA International} - Columbia, MD \hfill Summer 2012 - http://sra.com \\
        \textbf{RTGX - Ross Technology, Inc.} - Baltimore, MD \hfill Summer 2011 - http://rtgx.com \\
        \textbf{Computer Science Corporation} - Hanover, MD \hfill Summer 2011 - http://csc.com
    \end{asparadesc}

\section{\mysidestyle Education}
	\begin{compactdesc}
		\item[Rochester Institute of Technology] - Rochester, NY \rdate{September 2012 - Present}
		\begin{compactitem} { \small
			\item Major: Computer Science, Minor: American Politics
            \item Dean's List: In-Major: 3.82 GPA, Overall: 3.6 GPA
			\item Expected graduation: May 2016
		} \end{compactitem}
	\end{compactdesc}

\section{\mysidestyle Technical Skills \& Certifications}
	\begin{compactdesc}
		\item[Languages] \begin{inparaenum} { \small
            \item Scala
			\item Python
			\item Java
			\item Ruby
			\item Go
            \item Haskell
		} \end{inparaenum}
		\item[Tools] \begin{inparaenum} { \small
			\item Git
            \item Apache Spark
            \item Apache Avro
            \item Rails
            \item PostgreSQL
            \item JUnit
            \item Protocol Buffers
		} \end{inparaenum}
        \item[Certifications] \begin{inparaenum} { \small
            \item Cloudera Certified Developer for Apache Hadoop, 2012    
        } \end{inparaenum}
	\end{compactdesc}

\section{\mysidestyle Self-Directed Projects}
    \begin{asparablank}
        \item \textbf{Wikipedia Page Views}: Using HDFS and HBase, built a system that
            processed and stored the page view log data for all of Wikipedia 
            and presented the information in a real-time web UI. Personally setup and 
            maintained an 8 node Hadoop cluster for the project. \\
        \item \textbf{Github Language Analysis}: Built a data analyzer and
            ingest pipeline using Go to determine the programming language 
            usage across all of GitHub. This provided key insights to language usage
            trends over time and in comparison to each other. Implemented a 
            distributed ingest pipeline to increase processing capabilities. \\
        \item \textbf{LDAP Profiles}: Created and maintain a Rails web 
            application to act as a friendly interfreleasing to the end userIt integrates with WebAuth to securely provide keyless login. 
            Actively used in production at Rochester Institute of Technology.
    \end{asparablank}
\section{\mysidestyle Awards}
    \begin{asparablank}
        \item \textbf{Maryland Math Engineering Science Achievement}: Won 1st place
            in both regional and state level competitions for developing a maze
            traversal algorithm in Python. 
    \end{asparablank}
\section{\mysidestyle Clubs \& Activities}
    \begin{asparablank}
        \item \textbf{CSH (Computer Science House)}: An organization at RIT that
            provides a living and learning environment with access to unique facilities
            and hands-on learning, all in a social environment.
    \end{asparablank}
\end{resume}
\end{document}
